### 2024-05-30 doc/sections/introduction.tex
Spell check

Guglielmi \cite[\S4.1]{Guglielmi14:di} proves admissibility via the Splitting Theorem, which shows that proofs of conjoined structures can be split into separate subproofs. This is proved by a detailed syntactic analysis of proofs. Horne~\cite{Horne15:mav} gave a syntactic proof of the admissibility of the up fragment for MAV, that extends Guglielmi's technique with further reasoning about the additives. The proof is quite lengthy and involves intrincate syntactic reasoning and the subtle and complex termination measures.

We present an alternative proof of cut-elimination via a semantic model. This proof avoids some of the intrincacy of Horne's proof. We believe our proof to be more robust in the presence of extensions, due to our use of standard constructions such as Day monoids, order ideals, and the Chu construction. We demonsrate this by scaling down to plain BV and up to MAV with additive units.

@@

The phase semantic proof of cut-elimination does not easily extend to include the kind of self-dual connective present in BV and its extensions.
The phase space model derives duality by means of double negation with respect to the monoidal structure, which means that any connective has a derived dual. Attempts to extend the model with the non-commutative connective result in two distinct dual non-comutative connectives, reminiscent of the non-commutative tensor and par introduced by Slavnov~\cite{Slavnov19:scmll}.

>>>>

Guglielmi \cite[\S4.1]{Guglielmi14:di} proves admissibility via the Splitting Theorem, which shows that proofs of conjoined structures can be split into separate subproofs. This is proved by a detailed syntactic analysis of proofs. Horne~\cite{Horne15:mav} gave a syntactic proof of the admissibility of the up fragment for MAV, that extends Guglielmi's technique with further reasoning about the additives. The proof is quite lengthy and involves intricate syntactic reasoning and the subtle and complex termination measures.

We present an alternative proof of cut-elimination via a semantic model. This proof avoids some of the intricacy of Horne's proof. We believe our proof to be more robust in the presence of extensions, due to our use of standard constructions such as Day monoids, order ideals, and the Chu construction. We demonstrate this by scaling down to plain BV and up to MAV with additive units.

@@

The phase semantic proof of cut-elimination does not easily extend to include the kind of self-dual connective present in BV and its extensions.
The phase space model derives duality by means of double negation with respect to the monoidal structure, which means that any connective has a derived dual. Attempts to extend the model with the non-commutative connective result in two distinct dual non-commutative connectives, reminiscent of the non-commutative tensor and par introduced by Slavnov~\cite{Slavnov19:scmll}.
